Software Defect Prediction: Review, Commentary, and Future Work

### 2015-12-14 paper/paper.tex
Finished but still raw evaluation metrics section

The ROC curve is another fairly standard metric for performance used in the literature.  ROC, or Receiver Operating Characteristic analysis is an elaboration of the confusion matrix approach.  The idea is to use the rates of false positives and true positives on an x-y plane and to have x values represent the rates of false positives, and y values represent the rates of true positives.  The rate for a particular model can be plotted as point on the ROC curve and the area under the curve be used as a metric to determine the quality of the model with a point at (0,1) being optimal \cite{Posnett}.

These methods are used in a few of the papers we reviewed \cite{Rahman} \cite{Arisholm} \cite{Posnett}.  The ROC curve has somewhat diminished usage because of a number of downsides that have been discussed in several papers \cite{Hall}.

>>>>

The ROC curve is another fairly standard metric for performance used in the literature.  ROC, or Receiver Operating Characteristic analysis is an elaboration of the confusion matrix approach.  The idea is to use the rates of false positives and true positives on an x-y plane and to have x values represent the rates of false positives, and y values represent the rates of true positives.  The rate for a particular model can be plotted as point on the ROC curve and the area under the curve (AUC) be used as a metric to determine the quality of the model with a point at (0,1) being optimal \cite{Posnett}.

These methods are used in a few of the papers we reviewed \cite{Rahman} \cite{Arisholm} \cite{Posnett}.  Some negatives have been pointed out about the ROC approach and it's usefulness in certain circumstances.  One such negative is the fact that ROC curve approaches have "an overly optimistic view of an algorithm's performance if there is a large skew in the class distribution".  \cite{Davis}  Other papers mention the fact that both ROC/AUC approaches and confusion matrix based approaches in general do not address the whether a particular fault prediction methodology can pinpoint the source of the faults or not.  Since knowing where to find errors is just as important or more important than knowing whether errors exist or not several papers find ROC/AUC insufficient as an evaluation metric \cite{Posnett} \cite{Arisholm} \cite{Rahman}.

\subsection{Cost Effectiveness}

Arisholm et al \cite{Arisholm} contributed Cost Effectiveness as a metric to software defect prediction.  The high level idea behind Cost Effectiveness is the idea that it is impossible in most cases to inspect the entire code base of a large project for bugs. Defect prediction models that can guide inspection of code to find the largest number of bugs by inspecting the smallest percentage of the code base are viewed as models with high cost effectiveness.

The basic idea of the metric is a set of two curves on an x-y plane that has a percentage of faults as the y-axis, and the percentage of the lines of code included in classes selected to focus verification as the x-axis.  Classes are ranked according to their likelihood of having defects, first by the model, and next by the size of the class in case of ties.  The graph has a baseline of $y=x$ which is essentially the assumption that the percentage of faults will be equivalent to the percentage of lines of code inspected, this is done using a random ranking of the classes.  On the same graph is the cost effectiveness curve which is the actual percentage of faults given the percentage of LOC of class selected to focus verification according to the ranking determined by the model.

 Arisholm et al use an area calculation that is normalized to be a proportion of the optimal area under the curve.  To find an approximation of the optimal cost effectiveness they use a ranking that puts the most error filled classes towards the front and then create a cost effectiveness line according to that ranking.  The actual calculation is $CE_{\pi} = (CE_{pi}(model) - CE_{pi}(baseline))/ (CE_{pi}(optimal) - CE_{pi}(baseline))$  Other papers have used a simpler calculation of the area under the cost effectiveness curve, or AUCCE \cite{Posnett}.  The same concept is also used by Rahman et al under the name AUCEC \cite{Rahman}.

Those same papers that find ROC to be inefficient all suggest that Cost Effectiveness is an important and to some degree a superior metric to use in determining the performance of an algorithm \cite{Posnett} \cite{Arisholm} \cite{Rahman}.  The Arisholm paper was in fact one of the most influential papers that we worked with throughout the semester.  Cross-project defect prediction has been validated to some degree by the existence of Cost Effectiveness as an evaluation metric \cite{Rahman}.    The technique was used in Jiang et al as a metric as well \cite{Jiang}.
